Beam-Helicity and Beam-Charge Asymmetries\\ \red{Arising From} the DVCS and Bethe--Heitler \\ Processes \red{Using} a Proton Target \underline{Paper Tag: PDVCS0607 (v2.4)} \underline{Drafting Committee: DC90 (\today)}

### 2012-01-24 results_dual.tex
Updated the paper with the comments received from Dieter re his model

The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data analysis. The solid and dashed curves show results of calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab., and the collider experiments at H{\sc era}. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences. In this model, the $t$ dependence is approximated by a physically motivated Regge dependence. The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab.; the model fit represented by the dashed curves includes these data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the relevant amplitudes reported here are well described by the model.

>>>>

The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data analysis. The solid and dashed curves show results of calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab., and the collider experiments at H{\sc era}. The basic model~\cite{Mue05,Kum07,Kum08} is a \red{flexible GPD representation that is based on both a Mellin-Barnes integral and dispersion integral representation with weakly entangled skewedness and $t$ dependences}. The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Lab.; the model fit represented by the dashed curves includes these data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the relevant amplitudes reported here are well described by the model.
